Abstract

### 2022-04-06 paperwork/abstract/abstract.tex
yay
stuff

@@

>>>>

\textbf{2022:} \emph{Regional presenter at the Westchester Junior Science and Hummanities Fair}

\textbf{2022:} \emph{Virtual Powerpoint presenter at the Westchester Science and Engineering Fair (March)}

@@

\textbf{2022:} \emph{American Meteorological Society Award at the Westchester Science and Engineering Fair}
